Scaffolder - Simple and reproducable genome scaffolding using text configuration files.

### 2011-01-12 text/src/article.tex
Initial draft of abstract

\begin{abstract}
  \paragraph*{Background:} Background \dots
  \paragraph*{Methods:} Methods \dots
  \paragraph*{Results:} Results \ldots
  \paragraph*{Conclusions:} Conclusions \ldots
\end{abstract}

>>>>

\begin{abstract}

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented and non-contiguous final sequence. A common step in a genome
  sequencing project is finish the sequence be joining contigs together and
  filling gaps generated by PCR. This scaffolding step however is non-trivial
  as manipulating large blocks of fasta sequence is error-prone. Further more
  join sequences together in single fasta file hides the source of each region
  of sequence in the final genome build making reproducing the steps or
  editting an existing genome build difficult.

  \paragraph*{Methods:} Scaffolder is tool designed for scaffolding contigs
  togther to build a draft genome sequence. Scaffolder is implemented in the
  ruby programming language and is installed via the rubygem package management
  system. Genome scaffolds are written in YAML a markup language designed to be
  both human and machine readable. Command line binaries and extensive
  documentation are also available.

  \paragraph*{Results:} Scaffolder allows a genome build to be defined in in
  a scaffold file using a simple human readable syntax. The scaffold file
  highlights where each contig is used to build the draft genome sequence
  making the genome scaffolding reproducible. Changes and updates to the genome
  sequence are therefore comparatively easier to make compared to editing
  fasta. Scaffolder supports adding inserts to the scaffold to bridge gaps or
  replace regions in the scaffold. Scaffolder can be installed through the ruby
  gems.

  \paragraph*{Conclusions:} Conclusions \ldots Scaffolder represents an easy to
  use genome scaffolding tool. This tool promotes reproducibility and
  maintenence in building a genome. Scaffolder can be found at
  http://michaelbarton.me.uk/sfdr.

\end{abstract}
